Democracy, Public Support, and Measurement Uncertainty

### 2021-06-01 paper/dcpo_demsupport.Rmd
fixed the table format

date: "`r format(Sys.time(), '%B %d, %Y')`"
editor_options: 
  markdown: 
    wrap: sentence
tables: true # enable longtable and booktabs
citation_package: natbib
fontsize: 11pt
linestretch: 1.5 # double spacing using linestretch 1.5
bibliography: dcpo_demsupport.bib
# bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
      - \usepackage{fullpage}
      - \usepackage{lscape} #better for printing, page displayed vertically, content in landscape mode, \usepackage{pdflscape} better for screen, page displayed horizontally, content in landscape mode
---

@@

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools, mitools,
  boot, plm, # analysis
  flextable, 
  broomExtra, kableExtra, modelsummary, # tabulation
  gridExtra,
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse, janitor, glue, # data wrangling
  drhutools,
  dotwhisker, # visualization
  qs
)

@@

source(here::here("R", "tidy_pgmm.r"))
source(here::here("R", "moc_function.R"))

@@

# Theme setup
theme_set(theme_minimal())
```

@@

```{r dataInput, eval=TRUE}

claassen_replication <- readRDS("../data/claassen_replication.rds") %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)
load(here::here("data", "claassen_m5_theta.rda"))
load(here::here("data", "dem_mood_apsr.RData"))
# load(here::here("data", "dcpo_input.rda"))
# load(here::here("data", "dcpo_theta.rda"))
# load(here::here("data", "dcpo_sigma.rda"))

@@

```{r dcpoUncertaintyAJPS}
df_dcpo <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>%
    left_join(df_controls, by = c("country", "year")) %>% 
    mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

@@

```{r visualizeAJPS, fig.cap= "\\label{fig:visualizeAJPS}The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=10}

@@

```{r dcpoUncertaintyAPSR}
ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

df_dcpoUncertainAPSR <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>%
    left_join(df_controls, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

@@

ls_mod <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = df_dcpoUncertainAPSR)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = df_dcpoUncertainAPSR)")
)

@@

```{r visualizedAPSR, fig.cap= "\\label{fig:visualizedAPSR} The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}

load(here::here("output", "estimates_clsMeanAPSR.RDS"))
load(here::here("output", "estimates_clsAPSR.RDS"))
result_dcpoAPSR <- readRDS(here::here("output", "estimates_dcpoAPSR.RDS"))

@@

modelsummary(tb_result_cls,  
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex", 
             title = "Original") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

@@

@@

\begin{landscape}

@@

names(tb_result_clsAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM w. Corruption", "ECM w. Corruption-Regime", "FD w. Corruption", "FD w. Corruption-Regime")

@@

modelsummary(tb_result_clsAPSR, 
             stars = TRUE,
             coef_map = names_coef, 
             output = "latex") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

@@

names(tb_result_clsUncertainAPSR) <- c("ECM", "ECM-Regime", 
                          "FD", "FD-Regime", 
                          "ECM w. Corruption", "ECM w. Corruption-Regime", 
                          "FD w. Corruption", "FD w. Corruption-Regime")

@@

modelsummary(tb_result_clsUncertainAPSR, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

@@

names(tb_result_dcpoAPSR) <- c("ECM", "ECM-Regime", 
                          "FD", "FD-Regime", 
                          "ECM w. Corruption", "ECM w. Corruption-Regime", 
                          "FD w. Corruption", "FD w. Corruption-Regime")

@@

modelsummary(tb_result_dcpoAPSR, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

\pagebreak
```{r datawitherrors}

@@

\end{landscape}
# Replication with Alternative Methods Accounting for Uncertainty

```{r moc}

@@

>>>>

date: "`r format(Sys.time(), '%B %d, %Y')`"
editor_options: 
  markdown: 
    wrap: sentence
tables: true # enable longtable and booktabs
citation_package: natbib
fontsize: 11pt
linestretch: 1.5 # double spacing using linestretch 1.5
bibliography: dcpo_demsupport.bib
# bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
      - \usepackage{fullpage}
      - \usepackage{pdflscape} #\usepackage{lscape} better for printing, page displayed vertically, content in landscape mode, \usepackage{pdflscape} better for screen, page displayed horizontally, content in landscape mode
      - \newcommand{\blandscape}{\begin{landscape}}
      - \newcommand{\elandscape}{\end{landscape}}
---

@@

# load all the packages you will use below 
p_load(
  # data scrapping
  dataverse, 
  DCPOtools, mitools,
  boot, 
  here,
  # analysis
  plm, 
  rstan, 
  # presentation
  flextable, 
  broomExtra, 
  kableExtra, 
  modelsummary, 
  gridExtra,
  latex2exp,
  drhutools,
  dotwhisker, 
  # data wrangling
  tidyverse, 
  janitor, 
  glue, 
  qs
)

@@

source(here("R", "tidy_pgmm.r"))
source(here("R", "moc_function.R"))

@@

# Theme setup
theme_set(theme_minimal())

# Data input

claassen_replication <- readRDS("../data/claassen_replication.rds") %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)
load(here("data", "claassen_m5_theta.rda"))
load(here("data", "dem_mood_apsr.RData"))
load(here("data", "dcpo_input.rda"))
# load(here::here("data", "dcpo_theta.rda"))
# load(here::here("data", "dcpo_sigma.rda"))
# load(here("data", "dcpo_ajps_rubin.rda"))

@@

@@

```{r dcpoUncertaintyAJPS}
df_dcpo <- dcpo_ajps_rubin %>% map(~ .)

# df_dcpo <- purrr::map(1:1000, function(anEntry) {
#   dcpo_theta$theta[anEntry,,] %>% 
#     reformat_dcpo_output("theta") %>% 
#     left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
#               by = c("year", "country")) %>%
#     left_join(df_controls, by = c("country", "year")) %>% 
#     mutate(theta_dem = theta * regime,
#            theta_aut = theta * (1 - regime)) %>% 
#     plm::pdata.frame(index = c("country", "year"))
# })

@@

```{r visualizeAJPS, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=10}

@@

```{r dcpoUncertaintyAPSR}
# ls_country <- levels(dcpo_input$data$kk)
# first_year <- min(dcpo_input$data$year)
# 
# df_dcpoUncertainAPSR <- purrr::map(1:1000, function(anEntry) {
#   dcpo_theta$theta[anEntry,,] %>% 
#     reformat_dcpo_output("theta") %>% 
#     left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
#               by = c("year", "country")) %>%
#     left_join(df_controls, by = c("country", "year")) %>% 
#     plm::pdata.frame(index = c("country", "year"))
# })

@@

###Duble check the dataset--------------
ls_mod <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = df_dcpoUncertainAPSR)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = df_dcpoUncertainAPSR)")
)

@@

```{r visualizedAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}

load(here("output", "estimates_clsMeanAPSR.RDS"))
result_clsUncertainAPSR <- readRDS(here("output", "estimates_clsAPSR.RDS"))
result_dcpoAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))

@@

modelsummary(tb_result_cls,  
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex", 
             title = "Original") %>%

  kableExtra::kable_styling(font_size = 8) %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

@@

\blandscape

@@

@@

names(tb_result_clsAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")

@@

modelsummary(tb_result_clsAPSR, 
             stars = TRUE,
             coef_map = names_coef, 
             output = "latex") %>% 
  kableExtra::kable_styling(font_size = 7) %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

\elandscape

\blandscape

@@

names(tb_result_clsUncertainAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")

@@

modelsummary(tb_result_clsUncertainAPSR, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex") %>% 
  kableExtra::kable_styling(font_size = 7) %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

\elandscape

\blandscape

@@

names(tb_result_dcpoAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")

@@

modelsummary(tb_result_dcpoAPSR, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex") %>% 
  kableExtra::kable_styling(font_size = 7) %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

\elandscape

```{r datawitherrors}

@@

# Results Accounting for the Uncertainty in Both the Outcome and Explanatory Variables

```{r claassenFullUncertaintyAJPS}

load(here("data", "cls_ajps.rda")) # produced by cls_ajps_apsr_uncertain.R

result_clsUncertainFull <- map(ls_mod, function(aMod){ # reading a model
  result <- map(cls_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

names(result_clsUncertainFull) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

saveRDS(result_clsUncertainFull, file = here::here("output", "estimates_clsAJPSfullUncertain.RDS"))
```

```{r dcpoFullUncertaintyAJPS}
load(here("data", "dcpo_ajps.rda")) # produced by dcpo_ajps_apsr_uncertain.R

result_dcpoUncertainFull <- map(ls_mod, function(aMod){ # reading a model
  result <- map(dcpo_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

names(result_dcpoUncertainFull) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

saveRDS(result_dcpoUncertainFull, file = here::here("output", "estimates_dcpoAJPSfullUncertain.RDS"))
```

```{r visualizeFullUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy", eval = FALSE, fig.width=7.5, fig.height=10}

# Very weird phenomenon that the same type of rds files needs different ways to read
# Suggesting using the qs or csv data type in future.
result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_clsUncertainFull <- readRDS(here("output", "estimates_clsAJPSfullUncertain.RDS"))
result_dcpoUncertainFull <- readRDS(here("output", "estimates_dcpoAJPSfullUncertain.RDS"))

result_pooled <- bind_rows(
  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainFull$pooled[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainFull$pooled[[1]], model = "DCPO")
) %>% 
  mutate(type = "Pooled")

result_gmm <- bind_rows(
  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainFull$gmm[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainFull$gmm[[1]], model = "DCPO")
) %>% 
  mutate(type = "GMM")

result_regime <- bind_rows(
  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainFull$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainFull$`pooled-regime`[[1]], model = "DCPO")
) %>% 
  mutate(type = "Pooled")

result_regimeGmm <- bind_rows(
  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainFull$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainFull$`gmm-regime`[[1]], model = "DCPO")
) %>% 
  mutate(type = "GMM")

@@

```{r claassenFullUncertaintyAPSR}

load(here("data", "cls_apsr.rda")) # produced by cls_ajps_apsr_uncertain.R

ls_mod <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
)

result_clsFullUncertainAPSR <- map(ls_mod, function(aMod){ # reading a model
  result <- map(cls_apsr, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

names(result_clsFullUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(result_clsFullUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))

```{r dcpoFullUncertaintyAPSR}
load(here("data", "dcpo_apsr.rda")) # produced by cls_ajps_apsr_uncertain.R

###Duble check the dataset--------------
ls_mod <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
)

result_dcpoUncertainAPSR <- map(ls_mod, function(aMod){ # reading a model
  result <- map(dcpo_apsr, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

# Replication with Alternative Methods Accounting for Uncertainty
